PM\@: Information Security Management System

### 2022-03-21 ismsmemo/ismsmemo.tex
updated document class
Updated instructions

\documentclass[a4paper]{llncs}
\usepackage[utf8]{inputenc}
\usepackage[swedish]{babel}
\usepackage{csquotes}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[swedish]{cleveref}
\usepackage[single]{acro}
\usepackage[natbib,style=numeric-comp,maxbibnames=99,sorting=none]{biblatex}
\addbibresource{ismsmemo.bib}

@@

\begin{document}
\title{PM\@: Information Security Management System}
\author{%
  Carina Bengtsson and Lennart Franked
}
\institute{%
  Department of Information Systems and Technologies\\
  Mid Sweden University, Sundsvall
}
\date{\today}

@@

\subsection{Legal requirements according to MSBFS 2009:10}

In \iac{isms}, there are certain work tasks defined for the organisation.
The Swedish Civil Contingencies Agency (MSB) have defined in their statutes
MSBFS 2009:10~\cite{MSBFS2009:10}, which is binding for governmental agencies, 
stated that the governmental agencies should:
\begin{enumerate}
  \item To build an information security policy and other policy documents,
  \item elect one or several persons to lead and coordinate the work with
    information security,
  \item classify their information with a starting point in regard to
    confidentiality, integrity and availability,
  \item with the help of risk analysis, provide a risk evaluation, estimation
    and treatment, and
  \item document important audits and security measurements.
\end{enumerate}
Further more, in 5§ that

@@

If you are using the English course material, refer to the key-points a-i in
\cite[chap. 3.2.1]{iso27000}

@@

To implement \iac{isms} in an organisation is a large project. Therefore
the material mentions some success factors that are critical to achieve a
successful implementation \cite[3.6]{iso27000}. Give a short summary about
these success factors.

@@

\begin{enumerate}
  \item Information Security Management System;
    \begin{solution}
      Grade: F-C.
      \acp{isms} is described in \emph{Introduktion till 
        metodstödet}~\cite{MSB2011itm} or \cite[chap. 3]{iso27000},

      A management system can briefly be defined as:
      \begin{itemize}
        \item A \enquote{system} to manage the organization.
        \item Other example: Quality Management system, Environmental Management.
      \end{itemize}

      \Iac{isms} is a special case of a management system that cen briefly be
      explained as:
      \begin{itemize}
        \item \Iac{isms} is controlling the organizations information
          security. It also explains \emph{how} to work to manage the
          information security.

        \item Integrated with other management systems.
        \item There is an international standard for this: ISO 27000-series.
        \item MSBs 'Metodstöd' gives a description how to build \iac{isms} as
          an PDCA life cycle.
        \item \Iac{isms} should be adapted to the organizations need. MSB's
          \enquote{metodstöd} should be seen as a smorgasbord.
        \item The regulation MSBFS 2009:10~\cite{MSBFS2009:10} list what
          governmental agencies must implement, in regards to \acp{isms}.
      \end{itemize}
    \end{solution}

  \item Requirements according to MSBFS 2009:10, points 1--3 and one of the
    following key points 4--6. Or if you are using the english material,
    keypoints a-c and one the points d-i in \cite[chap. 3.2.1]{iso27000}.
    \begin{solution}
      Grade: F or P.

      Se MSBFS 2009:10~\cite{MSBFS2009:10}.
    \end{solution}

  \item Success factors; and
    \begin{solution}
      Grade: F-C.

      Described in \emph{Introduktion till metodstödet}~\cite{MSB2011itm}, avsnitt 
      2 \emph{Framgångsfaktorer}, or \cite[3.6]{iso27000}
      Success factors that needs to be mentioned are
      De framgångsfaktorer som ska beskrivas är
      \begin{itemize}
        \item Commitment from the management,
        \item Support through the entire organization,
        \item sufficient resources, and
        \item adapting the \ac{isms} to the organization.
      \end{itemize}
    \end{solution}

  \item Commitment from the Management
    \begin{solution}
      Grade: F eller P.

      Grading is not done solely on the student naming the suggestion given in
      the course literature, instead, it should be based on their own
      reflections.
    \end{solution}
\end{enumerate}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[swedish]{babel}
\usepackage{csquotes}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[swedish]{cleveref}
\usepackage[single]{acro}
\usepackage[natbib,style=numeric-comp,maxbibnames=99,sorting=none]{biblatex}
\addbibresource{ismsmemo.bib}

@@

\begin{document}
\title{PM\@: Information Security Management System}
\author{%
  Carina Bengtsson and Lennart Franked
}
\date{\today}

@@

\subsection{Legal requirements according to MSBFS 2020:6}

In \iac{isms}, there are certain work tasks defined for the organisation.
The Swedish Civil Contingencies Agency (MSB) have defined in their statutes
MSBFS 2020:6~\cite{MSBFS2020:6}, which is binding for governmental agencies, 
stated that the governmental agencies should:
\begin{enumerate}
  \item Ensure that there is an information security policy where the
        management's objectives and focus on
        the information security work are shown,
  \item Clarify the management and the rest of the organizations
        responsibilities, including the person or persons appointed to lead and coordinate
        information security work, and give these positions the
        powers needed,
  \item ensure that the information security work is assigned the necessary resources,
  \item establish the necessary internal rules, working methods and support 
  \item ensure that the content of the organisation's internal rules, working methods and support is
    evaluated and, if necessary, adapted.

\end{enumerate}
Further more, in 14§ that

@@

If you are using the English course material, refer to the key-points a-i in
\cite[chap. 4.2.1]{iso27000}

@@

To implement \iac{isms} in an organisation is a large project. Therefore
the material mentions some success factors that are critical to achieve a
successful implementation \cite[4.6]{iso27000}. Give a short summary about
these success factors.

@@

\begin{enumerate}
  \item Information Security Management System;
  \item Requirements according to MSBFS 2020:6, points 1--3 and one of the
    following key points 4--6. Or if you are using the english material,
    keypoints a-c and one the points d-i in \cite[chap. 4.2.1]{iso27000}.
  \item Success factors; and
  \item Commitment from the Management
\end{enumerate}

### 2022-03-21 ismsmemo/literature.tex
Updated instructions

% $Id$
% Author:	Daniel Bosk <daniel.bosk@miun.se>
Du ska inför skrivningen av detta PM ha läst dokumenten
\begin{itemize}
  \item \emph{Introduktion till metodstödet}~\cite{MSB2011itm},
  \item \emph{Säkra ledningens engagemang}~\cite{MSB2011sle}, och
  \item \emph{Projektplanering}~\cite{MSB2011p}.
\end{itemize}

>>>>

% $Id$
% Author:	Daniel Bosk <daniel.bosk@miun.se>, Lennart Franked
% <lennart.franked@miun.se>

Before starting this PM, you should have read the following documents:

\begin{itemize}
  \item \emph{Myndigheten för samhällsskydd och beredskaps föreskrifter om informationssäkerhet för
      statliga myndigheter}~\cite{MSBFS2020:6}
  \item \emph{Information technology – Security techniques – Information
security management systems – Overview and vocabulary (ISO/IEC 27000:2018)}~\cite[chap. 4]{iso27000}
(Use as a support document only, if you don't understand Swedish, use this as the main reference)
  \item \emph{Introduktion till metodstödet}~\cite{MSB2018iom}, och
  \item \emph{Ledningens engagemang avgörande}~\cite{MSB2018sle}
\end{itemize}

Alternatively
\begin{itemize}
  \item ISO 27000 standard~\cite[Chapter 4]{iso27000}
\end{itemize}
